Environmental stress affects niche breadth in plant-pollinator communities

### 2019-11-05 paper/manuscript.Rmd
more changes to intro:

Species interactions are known to vary widely across space and time. 
There are multiple examples of species that interact with a large number of partners in an ecological community or a particular season but with fewer in another. 
It has been proposed that some of variation can be attributed to environmental drivers. 
However, how exactly the environment, and the stress it imposes, affects the turnover of interactions is still unknown. 
It is crucial to understand why and how this turnover occur because the network of interactions of an ecological community is known to underpin ecosystem function and stability. 
Despite much progress in the last decades, we are still unable to predict species interactions, partially because we still have not accurately identified the factors that drive species to interact under certain conditions and not under another.

Species interactions are determined in part by niche processes (the matching of traits) and partly by neutral processes (more abundant species are more likely to encounter each other and, thus, interact). 
Both of these processes can be influenced by the environment. 
Therefore, it is not surprising that multiple studies have shown how changes to interactions, both pairwise and at the community level, can be driven by environmental change [@tylianakis_ecological_2017].
For instance, some studies show that the rate of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016]. 
Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
Overall,

There are two main processes involved in whether two species in a community interact or not.
The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species. 
Compared to other kinds of trophic interactions, mutualistic interactions, and plant-pollination interactions, in particular, are relatively generalised.
While a large proportion of the interactions appear to be opportunistic, a fraction of interactions shows a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017]. 
In contrast to opportunistic interactions with low trait-matching, the more co-evolved interactions with optimally matched traits are more persistent and presumably lead to a more substantial per-capita benefit for the interacting species. 
The second is a neutral process underpinned by the encounter rate of the interacting species. 
All else being equal, when the encounter rate of interacting species is high, there is a higher probability to interact than if the rate were lower, for example, due to species rarity.

Perhaps, because it operates at scales larger than those of the Eltonian niche concept, the abiotic environment is one of the factors that is commonly overlooked by community ecologists when explaining interaction turnover [but see @gravel_bringing_2018].

The most evident—and best-studied—way through which the environment can affect the structure of ecological networks is by way of patterns of community composition. 
At the heart of biogeography is the idea that the abiotic environment can determine the "Grinellian" niche of a species, this is whether the species can have a positive growth-rate when rare in a particular location.
For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Grinellian niche of both species.

Although less understood, the environment can also affect the interactions themselves, after community composition has been established [@tylianakis_ecological_2017]. 
For instance, some studies show that trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016], and both plant-plant [@bertness_positive_1994] and plant-pollinator [@tur_evaluating_2016] interactions can switch from facilitative to competitive along an elevation/temperature gradient. 
Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].

One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress. 
Previous research is so far equivocal and, taken together, suggest that environmental stress can have two contrasting effects on species' Eltonian-niche [@tylianakis_ecological_2017].
On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts they were best adapted to attack.
Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids.

@@

>>>>

Species interactions are known to vary widely across space and time. 
There are multiple examples of species that interact with a large number of partners in an ecological community or a particular season but with fewer in another. 
It has been proposed that at least some of this variation can be attributed to environmental drivers. 
Despite much progress in the last decades, we are still unable to predict species interactions, partially because we still have not accurately identified the factors that drive species to interact under certain conditions and not under another.

However, how exactly the environment, and the stress it imposes on species, affects wether two species interact or not, and ultimately species degree the number of partners a species has---its degree---is still unknown. 
It is crucial to understand why and how species degree might change because it underpins species importance and, collectively is the foundation of network structure that underpins ecosystem function and stability.

Species interactions are determined in part by niche processes (the matching of traits) and partly by neutral processes (more abundant species are more likely to encounter each other and, thus, interact). 
These two processes in turn 
Both of these processes can be influenced by the environment. 
Therefore, it is not surprising that multiple studies have shown how changes to interactions can be driven by environmental change [@tylianakis_ecological_2017].
For instance, some studies show that the rate of some trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016]. 
Contrastingly, other studies have shown either no overall effect or non-linear effects of temperature or precipitation on plant-pollinator interactions at the community level [@devoto_patterns_2005; @gravel_bringing_2018].

Each species can have multiple partners. 
Each of these partners, as well as the interactions with them, can be simultaneoulsy affected by the environmental conditions. 
Given all these sources of variation, it is not clear whether the environment can systematically affect species degree. 
Previous research suggests that there might be two alternative hypothesis of how the environment, in particular the environmental stress, affects the number of partners of a species [@tylianakis_ecological_2017]. 
On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts they were best adapted to attack.
Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids.

@@

<!-- There are two main processes involved in whether two species in a community interact or not. -->
<!-- The first is an "Eltonian" niche process that is underpinned by the traits of the interacting species.  -->
<!-- Compared to other kinds of trophic interactions, mutualistic interactions, and plant-pollination interactions, in particular, are relatively generalised. -->
<!-- While a large proportion of the interactions appear to be opportunistic, a fraction of interactions shows a strong signature of deep co-evolutionary history [@hutchinson_cophylogenetic_2017].  -->
<!-- In contrast to opportunistic interactions with low trait-matching, the more co-evolved interactions with optimally matched traits are more persistent and presumably lead to a more substantial per-capita benefit for the interacting species.  -->
<!-- The second is a neutral process underpinned by the encounter rate of the interacting species.  -->
<!-- All else being equal, when the encounter rate of interacting species is high, there is a higher probability to interact than if the rate were lower, for example, due to species rarity.  -->

<!-- Perhaps, because it operates at scales larger than those of the Eltonian niche concept, the abiotic environment is one of the factors that is commonly overlooked by community ecologists when explaining interaction turnover [but see @gravel_bringing_2018].  -->

<!-- The most evident—and best-studied—way through which the environment can affect the structure of ecological networks is by way of patterns of community composition.  -->
<!-- At the heart of biogeography is the idea that the abiotic environment can determine the "Grinellian" niche of a species, this is whether the species can have a positive growth-rate when rare in a particular location. -->
<!-- For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Grinellian niche of both species.  -->

<!-- Although less understood, the environment can also affect the interactions themselves, after community composition has been established [@tylianakis_ecological_2017].  -->
<!-- For instance, some studies show that trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016], and both plant-plant [@bertness_positive_1994] and plant-pollinator [@tur_evaluating_2016] interactions can switch from facilitative to competitive along an elevation/temperature gradient.  -->
<!-- Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018]. -->

<!-- One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress.  -->
